Breanna_Code

### 2022-09-29 Draft_Report.Rmd
first commit

We are going to use a markdown document to communicate draft code and results, to try and setup a template for how we would report on these data to a client.

>>>>

Here we are going to use a markdown document to communicate draft code and results, to try and setup a template for how we would report on these data to a client.
